Figures

### 2019-07-29 figures/07_model-selection.Rmd
highlight re

gg_tp_fe <- ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
    geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment")

gp <- ggplotGrob(gg_tp_fe)
facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
x.var         <- sapply(ggplot_build(gg_tp_fe)$layout$panel_scales_x,
                function(l) length(l$range$range))
gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
gg_tp_fe <- ggplotify::as.ggplot(gp)
gg_tp_fe
```

@@

gp <- ggplotGrob(gg_tn_fe)
facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
x.var         <- sapply(ggplot_build(gg_tn_fe)$layout$panel_scales_x,
                function(l) length(l$range$range))
gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
gg_tn_fe <- ggplotify::as.ggplot(gp)
gg_tn_fe
```

@@

gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
  theme(legend.position = 0)

@@

@@

```{r fe}
cowplot::plot_grid(gg_tp_fe + theme(axis.title.x = element_blank()), 
                   gg_tn_fe + theme(axis.text.y = element_blank(), 
                                    axis.title.x = element_blank()), 
                   rel_widths = c(1, 1))
```

```{r re}
cowplot::plot_grid(gg_tp_re, 
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank()), 
                   rel_widths = c(1, 0.9))
```

>>>>

gg_tp_fe <- 
  ggplot(data = gg_tp) + 
  geom_pointrange(aes(x = pretty, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) + 
  expand_limits(y = -1.8) +
  geom_rect(ymin = -0.6, ymax = -0.6 - 2, xmin = 0, xmax = nrow(gg_tp) + 1, 
              fill = "transparent") +
  geom_text(aes(x = pretty, label = pretty, color = signif), 
            y = -0.65, vjust = 0.5, hjust = "right") + 
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  geom_hline(yintercept = 0) +
  scale_y_continuous(breaks = seq(from = -0.6, to  = 0.4, by = 0.2), 
                     labels = scales::number_format(accuracy = 0.1)) +
  coord_flip() +
  theme(axis.text.y = element_blank(), 
        axis.ticks.y = element_blank(), 
        axis.title.y = element_blank()) + 
    facet_wrap(~category, strip.position = "left", ncol = 1, scales = "free_y",
               as.table = FALSE) +
    theme(panel.spacing = unit(0, "lines"), 
          strip.placement = "outside", 
          strip.background = element_blank(), 
          axis.title.y = element_blank()) + 
        ylab("Standardized slope") + theme(legend.position = 0) + 
        ggtitle("TP") + xlab("") +
  theme(panel.background = element_rect(fill = "transparent", color = NA),
        plot.background = element_rect(fill = "transparent", color = NA), 
        panel.grid = element_blank(),
        rect = element_rect(fill = "transparent")) + 
    annotate(x=0, xend=0, y=-0.6, yend=0.4, 
             colour="black", lwd=0.9, geom="segment") 
```

@@

equalize_panels <- function(x){
  gp <- ggplotGrob(x)
  facet.columns <- gp$layout$t[grepl("panel", gp$layout$name)]
  x.var         <- sapply(ggplot_build(x)$layout$panel_scales_x,
                  function(l) length(l$range$range))
  gp$heights[facet.columns] <- gp$heights[facet.columns] * rev(x.var)
  x <- ggplotify::as.ggplot(gp)
  x
}
```

@@

gg_tn_re <- ggplot(data = fit_tn$re) +
  geom_hline(yintercept = as.numeric(fit_tn$re_global["50%"])) +
  geom_pointrange(aes(x = hu4vzoneid, y = `50%`, 
                      ymin = `5%`, ymax = `95%`, color = signif)) +
  scale_color_manual(values = c("FALSE" = "black", "TRUE" = "red")) +
  coord_flip() +
  cowplot::theme_cowplot() +
  theme(rect = element_rect(fill = "transparent")) +
  ggtitle("TN ~ corn slope") + xlab("Zone ID") + ylab("") +
  theme(legend.position = 0)

@@

```{r fe}
cowplot::plot_grid(
  equalize_panels(
    gg_tp_fe + theme(axis.title.x = element_blank())
  ), 
  equalize_panels(
    gg_tn_fe + 
      theme(axis.text.y = element_blank(), 
            axis.title.x = element_blank())), 
  rel_widths = c(1, 1))
```

@@

```{r re}
cowplot::plot_grid(gg_tp_re, 
                   gg_tn_re + theme(axis.text.y = element_blank(), 
                                    axis.title.y = element_blank()), 
                   rel_widths = c(1, 0.9))

cowplot::plot_grid(gg_tp_re, 
                   gg_tn_re + 
                     theme(axis.text.y = element_blank(), 
                           axis.title.y = element_blank()) + 
                     gghighlight(max(`50%`), n = 1), 
                   rel_widths = c(1, 0.9))
```
